---
title: "PCR.avg.brayC"
author: "Joe Duprey"
date: "10/1/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(dplyr)
library(vegan)
```

## Data Exploration and Visualization 
## Working Towards Research Question for HC/SJ Data

psuedocode 
later) get read avgs, this time accounting for the fact that there are 2 PCR reps
and 3 PCR reps

1) calculate eDNA index, also account for non detections THEN do BC dissimilarity

2) recreate basic boxplots of bethic communities, maybe look into the insect
data that Ryan keeps mentioning

3) Bray Curtis and Jaccard heatmaps could be interesting 

4) In another script: recreating Moncho's k-means analysis -> this begins at line 369 of manuscript.main.analysis

## calculate eDNA index with absences included
does this even make a difference for BC? 

```{r}
eDNAindex <- read.csv("../data/eDNAindex.avg.reps.csv")

eDNAindex.PA <- eDNAindex %>%
  select(sample, species, eDNA_index) %>%
  pivot_wider(names_from=sample, values_from=eDNA_index, values_fill=list(eDNA_index=0))

eDNAindex.PA <- eDNAindex.PA %>%  
  pivot_longer(!species, names_to='sample', values_to='eDNA_index') 

# why does NA show up here
Index.check.PA <- eDNAindex.PA %>% 
  group_by(species) %>% 
  summarize(max(eDNA_index),
            min(eDNA_index))

Index.check <- eDNAindex %>%
  group_by(species) %>% 
  summarize(max(eDNA_index),
            min(eDNA_index))
```

## Including Plots

```{r}
data(varespec)
```

